---
title: "IS607 Week 2"
author: "Rob Hodde"
date: "February 7, 2016"
output: html_document
---

Please place your solution in a single R Markdown (.Rmd) file, post your code to GitHub, and publish your
markdown to rpubs.com, and then include the URLs of your GitHub repository and your rpubs.com code in your
week 3 assignment link. You should also have the original data file accessible through your code-for example,
stored in a GitHub repository and referenced in your code.

Very often, we're tasked with taking data in one form and transforming it for easier downstream analysis. Over the
next few weeks, we'll work with several packages that help with the tasks of tidying and transforming data.

UCI Machine Learning Repository. 

University of California Irvine maintains an archive of datasets.

1 Your task is to choose one dataset, then study the data and its associated description of the data (i.e. "data dictionary"). You
should take the data, and create an R data frame with a subset of the columns (and if you like rows) in the dataset.
Your deliverable is the R code to perform these transformation tasks.

If you need help in choosing a dataset, you might choose "Pittsburgh Bridges" here:
https://archive.ics.uci.edu/ml/datasets/Pittsburgh+Bridges. 


```{r}

sURL <- "https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/bridges.data.version1"
dfBridges <- read.table(file = sURL, header = FALSE, sep = ",", stringsAsFactors = FALSE)
head(dfBridges)  # verification

```

Now we will place the attribute names in the data frame.  

```{r}

colnames(dfBridges) <- c("IDENTIF","RIVER","LOCATION","ERECTED","PURPOSE","LENGTH","LANES", "CLEAR-G", "T-OR-D", "MATERIAL","SPAN","REL-L","TYPE")

str(dfBridges)

```

Now we will create a dataframe with a subset of the columns and rows.  

```{r}

dfLongBridges <- subset(dfBridges, dfBridges$SPAN == "LONG", select = c(IDENTIF, PURPOSE, LENGTH, SPAN))
dfLongBridges

```




   
   